Pillar 2 - (STM) Topic Modeling

### 2019-03-28 Pillar 2 -(STM) Topic Modeling.Rmd
titles

#clean
rm(findK, k_topics)
```
###From stm_eval
```{r manual eval plots}

plot_eval <- function(origin){
stm_eval_model %>%
  filter(Origin == origin) %>%
  transmute(n_topic,
            `Lower bound` = lbound,
             Residuals    = map_dbl(residual, "dispersion"),
            `Semantic coherence` = map_dbl(semantic_coherence, mean),
            `Held-out likelihood` = map_dbl(eval_heldout, "expected.heldout")) %>%
  gather(Metric, Value, -n_topic) %>%
  ggplot(aes(n_topic, Value, color = Metric)) +
  geom_line(size = 1.5, alpha = 0.7, show.legend = FALSE) +
  geom_point()+
  facet_wrap(~Metric, scales = "free_y") +
  labs(x = "Number of Topics)",
       y = NULL,
       title = "Model diagnostics by number of topics")
}

plot_eval("manuals")
plot_eval("overview")
```

>>>>

#clean
rm(findK, k_topics)
```
###From stm_eval
```{r manual eval plots}
#Function
plot_eval <- function(origin){
stm_eval_model %>%
  filter(Origin == origin) %>%
  transmute(n_topic,
            `Lower bound` = lbound,
             Residuals    = map_dbl(residual, "dispersion"),
            `Semantic coherence` = map_dbl(semantic_coherence, mean),
            `Held-out likelihood` = map_dbl(eval_heldout, "expected.heldout")) %>%
  gather(Metric, Value, -n_topic) %>%
  ggplot(aes(n_topic, Value, color = Metric)) +
  geom_line(size = 1.5, alpha = 0.7, show.legend = FALSE) +
  geom_point()+
  facet_wrap(~Metric, scales = "free_y") +
  labs(x = "Number of Topics)",
       y = NULL,
       title = "Model diagnostics by number of topics")
}

#Create plots
plot_eval("manuals")
plot_eval("overview")
```
